---
title: "Ale's ideas"
author: "Alejandra Garcia Isaza"
date: "5/21/2020"
output: html_document
---

Some questions: https://www.childhealthdata.org/learn-about-the-nsch/topics_questions/2017-nsch-guide-to-topics-and-questions 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rio)
library(here)

theme_set(theme_minimal())
```

```{r}
NCSH <- import(here("data","2017-2018 NSCH_Topical_DRC_Dec 2019.csv"), setclass = "tbl_df")

state <- import(here("data","fips_state.csv"))

# Left_join to add states in the NCSH dataset
final_data <- left_join(NCSH, state, by = "FIPSST")
```

```{r}
# data prep

selected_data <- final_data %>%
  select(HHID, HHLANGUAGE, SC_AGE_YEARS, SC_SEX, MOMAGE, HHCOUNT, K6Q20, K11Q60, K11Q61, K11Q62, S9Q34, K10Q14, ACE1, ACE3, ACE4, ACE5, ACE6, ACE7, ACE8, ACE9, ACE10, RECOGABC, A1_GRADE, A2_GRADE, K6Q60_R, K6Q61_R, FOODSIT, K8Q30, CONFIDENT, povlev4_1718, AdultEduc_1718, WrkngPoor_1718, ACEct_1718, ACE2more_1718, State) %>%
  janitor::clean_names() %>% # cleaning names
  filter(sc_age_years == 5) # filtering for 5 years old
```

values of missing data:

a2_grade # this one has missing data as 95 and 99
foodsit # this one has missing data as 99
k6q60_r # this one has missing data as 90
wrkng_poor_1718 # this one has missing data as 99

```{r}
# creating a function to recode missing data

# vector with missing values in my dataset
missing_vals <- c(90, 95, 99)

# function that returns true if values in vector are equal to missing_vals. The function takes a vector x, and specified values of missing data
recode_missing <- function(x, missing_vals = c(90, 95, 99)) {
  test <- x %in% missing_vals
  ifelse(test, NA, x)
}

# function that recodes missing values to NA. The function takes a dataframe with variables with missing data, and specified values of missing data
recode_missing_df <- function(df, missing_vals = c(90, 95, 99)) {
  modify(df, ~recode_missing(.x, missing_vals)) # here uses the function created above
}

d <- recode_missing_df(selected_data) %>%
  drop_na() # dropping cases with missing data
```

* SELECTED QUESTIONS *
 

1. DURING THE PAST WEEK, how many days did you or other family members tell stories or sing songs to this child? (k6q61_r)

0 days
1-3 days
4-6 days
Every day

```{r}
d$k6q61_r %>%
  range()
```

2. DURING THE PAST WEEK, how many days did you or other family members read to this child? (k6q60_r)

0 days
1-3 days
4-6 days
Every day

```{r}
d$k6q60_r %>%
  range()
```

3. How confident are you that this child is ready to be in school? (confident)

Completely confident
Mostly confident
Somewhat confident
Not at all confident

```{r}
d$confident  %>%
  range()
```

4. How well do you think you are handling the day-to-day demands of raising children? (k8q30)

Very well
Somewhat well
Not very well
Not at all

```{r}
d$k8q30 %>%
  range()
```

5. Poverty level of this household based on DHHS guidelines - Imputed

note: I couldn't find the labels for the responses

```{r}
d$povlev4_1718 %>%
  range()
```

6. What is the highest grade or level of school you have completed? Mark (X) ONE box. (a1_grade)
note: this is adult 1 or primary caregiver. 

8th grade or less
9th-12th grade; No diploma
High School Graduate or GED Completed
Completed a vocational, trade, or business school program
Some College Credit, but no Degree
Associate Degree (AA, AS)
Bachelor’s Degree (BA, BS, AB)
Master’s Degree (MA, MS, MSW, MBA)
Doctorate (PhD, EdD)

```{r}
d$a1_grade %>%
  range()
```

```{r}
# creating a list for each education level with all the variables - base way:
# by_ed_level <- split(d, d$a1_grade)

# using nest to create list columns
by_ed_level <- d %>%
    nest(-a1_grade)

by_ed_level

str(by_ed_level$data)
```
```{r}
d2 <- by_ed_level %>%
    mutate(m1 = map(data, ~lm(confident ~ k6q60_r, data = .x)),
           coefs = map(m1, coef))

d2$coefs[[9]]
```

```{r}
# plot 

ggplot(d, aes(factor(k6q60_r), factor(confident))) +
  geom_jitter(color = "purple") +
  facet_wrap(~a1_grade)

```

