---
title: "spring20_finalproject"
author: "Asha Yadav"
date: "4/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rio)
library(here)
library(naniar)
library(colorblindr)
library(plotly)
library(tigris)
library(geofacet)
library(cowplot)
library(ggrepel)
library(ggalt)
library(forcats)

theme_set(theme_minimal())

```

```{r}
# importing the data

NCSH <- import(here("data","2017-2018 NSCH_Topical_DRC_Dec 2019.csv"), setclass = "tbl_df")
state <- import(here("data","fips_state.csv"))
# Left_join to add states in the NCSH dataset

final_data <- left_join(NCSH, state, by = "FIPSST")


```


```{r}
# Filtering data for under 5 year old children.
data_under5 <- final_data %>%
  select(State, SC_CSHCN, ACE2more_1718, SC_AGE_YEARS) %>%
  filter(SC_AGE_YEARS <= 5)

# Changing numeric variables to character

data_under5$SC_CSHCN[which(data_under5$SC_CSHCN==1)]<- "Sp Health Needs" # Make this a function (05.22.20)
data_under5$SC_CSHCN[which(data_under5$SC_CSHCN==2)]<-"No Sp Health needs"

data_under5$ACE2more_1718[which(data_under5$ACE2more_1718==1)]<-"Exp No ACE"
data_under5$ACE2more_1718[which(data_under5$ACE2more_1718==2)]<-"Exp 1 ACE"
data_under5$ACE2more_1718[which(data_under5$ACE2more_1718==3)]<-"Exp 2 ACE"

# Removing missing data

data_under5 <- data_under5 %>% # Make this a function (05.22.20)
  replace_with_na(replace = list(ACE2more_1718 = 99)) %>%
  drop_na()

# count adverse childhood experiences

data_under5 <- data_under5 %>%
  select(State, SC_CSHCN, ACE2more_1718) %>%
  group_by(State, SC_CSHCN) %>%
  count(ACE2more_1718)

# percentage

data_under5 <- data_under5 %>% # Make this a function (05.22.20)
  mutate(Percentage = (n/sum(n))*100)

```


```{r,  fig.height=9, fig.width=9}

data_under5$region <- recode(data_under5$State,
                              "California" = "West Coast",
                              "Oregon" = "West Coast",
                              "Alaska" = "West Coast",
                              "Washington" = "West Coast")

p1 <- data_under5 %>% 
  group_by(State) %>% 
  filter(region == "West Coast") %>% 
  ungroup() %>% 
ggplot(aes(fct_reorder(State, Percentage), Percentage)) +
  geom_col(aes(fill = ACE2more_1718), position = "dodge") +
  coord_flip() +
  facet_wrap(~SC_CSHCN) +
  theme(strip.text.x = element_text(size=8),
        strip.background = element_rect(color = "black"),
        legend.position = "none",
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        text = element_text(size = 8),
        legend.title = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank()) +
  theme(plot.title = element_text(hjust = 0.50)) +
  scale_fill_brewer(palette = "Set2")

data_under5$region <- recode(data_under5$State,
                             "New York" = "East Coast",
                             "New Jersey" = "East Coast",
                             "Massachusetts" = "East Coast",
                             "Pennsylvania" = "East Coast")

p2 <- data_under5 %>% 
  group_by(State) %>% 
  filter(region == "East Coast") %>% 
  ungroup() %>% 
ggplot(aes(fct_reorder(State, Percentage), Percentage)) +
  geom_col(aes(fill = ACE2more_1718), position = "dodge") +
  coord_flip() +
  facet_wrap(~SC_CSHCN) +
  theme(strip.text.x = element_text(size=8),
        strip.background = element_rect(color = "black"),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        text = element_text(size = 8),
        legend.title = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank()) +
  theme(plot.title = element_text(hjust = 0.10)) +
  scale_fill_brewer(palette = "Set2")

plot_row <- plot_grid(p1, p2, ncol=1, labels = c())

title <- ggdraw() + 
  draw_label(
    "Children under 5 with special health needs likely to experience 1 or more adverse\n childhood experiences in East and West Coast (Data Source: NSCH 2016 & NSCH 2017)",
    x = 0, hjust = 0) + 
  theme(
    plot.margin = margin(0, 0, 0, 7)
    )
  
plot_grid(
  title, plot_row,
  ncol = 1,
  rel_heights = c(0.1, 1)
  )


```

```{r,fig.width=20, fig.height=15}

# Use pmap to create more than 2 plots - try using nest() and mutate (05.22.20)
ggplot(data_under5, aes(x = ACE2more_1718,
                        y = Percentage,
                        fill = SC_CSHCN)) +
  geom_col(position = "dodge") +
  coord_flip() +
  theme_bw() +
  facet_geo(~State) +
  theme_bw() +
  theme(strip.text.x = element_text(size=15),
        strip.background = element_rect(color = "black"),
        axis.title.y = element_blank(),
        text = element_text(size = 20),
        legend.title = element_blank()) +
  labs(title = "Children under 5 with special health needs likely to experience higher adverse childhood experiences",
       caption = "Data Source: NSCH 2017-18 data") +
  scale_fill_OkabeIto()

```

```{r, fig.height= 10, fig.width = 12}
# Dataset for year 2017 and 2016
# Joined dataset with FIPSST dataset

NCSH_17_p2 <- NCSH%>%
  select(FIPSST, SC_CSHCN, ACE2more_1718, SC_AGE_YEARS, ACEdivorce_1718, ACEdeath_1718, ACEjail_1718, ACEdomviol_1718, ACEneighviol_1718, ACEmhealth_1718, ACEdrug_1718 )%>%
  filter(SC_AGE_YEARS <= 5, SC_CSHCN == 1, ACE2more_1718 == 1 ) %>%
  rename(SC_CSHCN_1718 = "SC_CSHCN")

NCSH_17_p2 <- left_join(NCSH_17_p2, state, by = "FIPSST")

NCSH_17_p2 <- NCSH_17_p2 %>%
  select(State, ACE2more_1718) %>%
  group_by(State) %>%
  count()%>%
  rename(ACE_17 = "n")

NCSH_16_p2 <- import(here("data","2016NSCHTopical_DRCv3_Sep2018.csv")) %>%
  select(FIPSST, SC_CSHCN, ACE2more_16, SC_AGE_YEARS, ACEdivorce_16, ACEdeath_16, ACEjail_16, ACEdomviol_16, ACEneighviol_16, ACEmhealth_16, ACEdrug_16) %>%
  filter(SC_AGE_YEARS <= 5, SC_CSHCN == 1, ACE2more_16 ==1) %>%
  rename(SC_CSHCN_16 = SC_CSHCN)

NCSH_16_p2 <- left_join(NCSH_16_p2, state, by = "FIPSST") %>%
  select(State, ACE2more_16) %>%
  group_by(State) %>%
  count() %>%
  rename(ACE_16 = "n")

# Joined datased for 2017 and 2016 in one dataset and filtered state
data_1618 <- full_join(NCSH_17_p2, NCSH_16_p2, by = "State") %>%
  filter(State%in%c("Alaska", "Oregon", "Washington", "California", "New York", "New Jersey", "Massachusetts", "Pennsylvania"))

# PLot to compare Advere childood experiences in children with special health needs from 2016 to 2017 in selected states

library(scales)
theme_set(theme_classic())

colnames(data_1618) <- c("State", "ACE_16", "ACE_17")
left_label <- paste(data_1618$State, round(data_1618$`ACE_16`),sep=", ")
right_label <- paste(data_1618$State, round(data_1618$`ACE_17`),sep=", ")
data_1618$class <- ifelse((data_1618$`ACE_17` - data_1618$`ACE_16`) < 0, "red", "green")

# Plot

p2 <- ggplot(data_1618) + geom_segment(aes(x=1, xend=2, y=`ACE_16`, yend=`ACE_17`,
                                          col=class), size= 1, show.legend=F) + 
  geom_vline(xintercept=1, linetype="dashed", size=.5) +
  geom_vline(xintercept=2, linetype="dashed", size=.5) +
  scale_color_manual(labels = c("Up", "Down"),
                     values = c("green"="#00ba38", "red"="#f8766d")) +
  labs(x="", y="Number of children", 
       title = "Number of reported Sp Health needs children with Adverse Childhood Experiences (birth to 5) in\nEast Coast and West Coast\n") +
  xlim(.5, 2.5) + ylim(0,(1.1*(max(data_1618$`ACE_16`, data_1618$`ACE_17`))))

# Add texts
p2 <- p2 + geom_text(label=left_label, y=data_1618$`ACE_16`, x=rep(1, NROW(df)), 
                     hjust=1.1, size=5)
p2 <- p2 + geom_text_repel(label=right_label, y=data_1618$`ACE_17`, x=rep(2, NROW(df)),
                     hjust=-0.1, size=5)
p2 <- p2 + geom_text(label="TIME 1 (2016)", x=1, y=1.1*(max(data_1618$`ACE_16`,
                                                     data_1618$`ACE_17`)), 
                     hjust=1.2, size=5)
p2 <- p2 + geom_text(label="TIME 2 (2017)", x=2, y=1.1*(max(data_1618$`ACE_16`,
                                                     data_1618$`ACE_17`)), 
                     hjust=-0.1, size=5)  

p2 + theme(panel.background = element_blank(), 
           panel.grid = element_blank(),
           axis.ticks = element_blank(),
           axis.text.x = element_blank(),
           panel.border = element_blank(),
           axis.text.y = element_text(size = 10),
           axis.title = element_text(size = 10),
           plot.title = element_text(color = "black", size = 15, 
                                     face = "bold", hjust = 0.5 ),
           plot.margin = unit(c(2,4,2,4), "cm"))
  

```



Final Project Components

* No code is used repetitively (no more than twice) [10 points]
* More than one variant of purrr::map is used [10 points]
* At least one {purrr} function outside the basic map family (walk_*, reduce, modify_*, etc.) [10 points]
* At least one instance of parallel iteration (e.g., map2_*, pmap_*) [10 points]
* At least one use case of purrr::nest %>% mutate() [10 points]
* At least two custom functions [20 points; 10 points each]
  ** Each function must do exactly one thing
  ** The functions may replicate the behavior of a base function - as noted above this is about practicing the skills you learn in class
* Code is fully reproducible and housed on GitHub [10 points]
* No obvious errors in chosen output format [10 points]
* Deployed on the web and shareable through a link [10 points]


```{r}

# 1 custom function on missing data (by Ale), nest, mutate and map2 to produce plot for 51 states (by Asha)

selected_data <- final_data %>%
  select(HHID, HHLANGUAGE, SC_AGE_YEARS, SC_SEX, MOMAGE, HHCOUNT, K6Q20, K11Q60, K11Q61, K11Q62, S9Q34, K10Q14, ACE1, ACE3, ACE4, ACE5, ACE6, ACE7, ACE8, ACE9, ACE10, RECOGABC, A1_GRADE, A2_GRADE, K6Q60_R, K6Q61_R, FOODSIT, K8Q30, CONFIDENT, povlev4_1718, AdultEduc_1718, WrkngPoor_1718, ACEct_1718, ACE2more_1718, State) %>%
  janitor::clean_names() %>% # cleaning names
  filter(sc_age_years <= 5, ace2more_1718 > 1) # filtering for 5 years old

selected_data1 <-selected_data %>%
  select(state, ace2more_1718)

# creating a function to recode missing data

# vector with missing values in my dataset
missing_vals <- c(90, 95, 99)

# function that returns true if values in vector are equal to missing_vals. The function takes a vector x, and specified values of missing data
recode_missing <- function(x, missing_vals = c(90, 95, 99)) {
  test <- x %in% missing_vals
  ifelse(test, NA, x)
}

# function that recodes missing values to NA. The function takes a dataframe with variables with missing data, and specified values of missing data
recode_missing_df <- function(df, missing_vals = c(90, 95, 99)) {
  modify(df, ~recode_missing(.x, missing_vals)) # here uses the function created above
}

selected_data1 <- recode_missing_df(selected_data1) %>%
  drop_na() %>%
  mutate(ACE = factor(ace2more_1718),
         ACE = recode_factor(ACE,
                          "2" = "Exp 1 ACE",
                          "3" = "Exp 2 Ace"))

selected_data1 <- selected_data1 %>%
  group_by(state, ACE) %>%
  count(ACE)


#Plot for one state

selected_data1 %>%
  filter(state == "Alabama")

ggplot(selected_data1, aes(ACE, n)) +
  geom_col(aes(fill = n)) +
  scale_fill_distiller(type = "seq",
                       limits = c(0, max(selected_data1$n)),
                       palette = "BuPu",
                       direction = 1) +
  ylim(0, max(selected_data1$n)) +
  coord_flip() +
  labs(title = "Number of Adverse Childhood Experiences: Alabama",
       x = "Adverse Childhood Exp.")

#Nest data and mutate

selected_data1 %>%
  group_by(state) %>%
  nest() %>%
  mutate(plot = map(data, ~
                      ggplot(.x, aes(ACE, n)) +
                      geom_col(aes(fill = n)) +
                      scale_fill_distiller(type = "seq",
                                           limits = c(0, max(selected_data1$n)),
                                           palette = "BuPu",
                                           direction = 1) +
                      ylim(0, max(selected_data1$n)) +
                      coord_flip() +
                      labs(title = "Adverse Childhood Experiences")
                    )
         )

# Plot for all states
library(glue)

P <- selected_data1 %>%
  group_by(state) %>%
  nest() %>%
  mutate(plot = map2(data, state, ~
                       ggplot(.x, aes(ACE, n)) +
                       geom_col(aes(fill = n)) +
                       scale_fill_distiller(type = "seq",
                                            limits = c(0, max(selected_data1$n)),
                                            palette = "BuPu",
                                            direction = 1) +
                       ylim(0, max(selected_data1$n)) +
                       coord_flip() +
                       labs(title = glue("Adverse Childhood Exp : {.y}"))
                       )
         )
P

P$plot[[10]]
```

```{r}

# 1 custom function on missing data, nest, mutate and pmap to produce plot for 51 states (by Asha)

selected_data <- final_data %>%
  select(HHID, HHLANGUAGE, SC_AGE_YEARS, SC_SEX, MOMAGE, HHCOUNT, K6Q20, K11Q60, K11Q61, K11Q62, S9Q34, K10Q14, ACE1, ACE3, ACE4, ACE5, ACE6, ACE7, ACE8, ACE9, ACE10, RECOGABC, A1_GRADE, A2_GRADE, K6Q60_R, K6Q61_R, FOODSIT, K8Q30, CONFIDENT, povlev4_1718, AdultEduc_1718, WrkngPoor_1718, ACEct_1718, ACE2more_1718, State) %>%
  janitor::clean_names() %>% # cleaning names
  filter(sc_age_years <= 5, ace2more_1718 > 1) # filtering for 5 years old

selected_data1 <-selected_data %>%
  select(state, ace2more_1718)

# creating a function to recode missing data

# vector with missing values in my dataset
missing_vals <- c(90, 95, 99)

# function that returns true if values in vector are equal to missing_vals. The function takes a vector x, and specified values of missing data
recode_missing <- function(x, missing_vals = c(90, 95, 99)) {
  test <- x %in% missing_vals
  ifelse(test, NA, x)
}

# function that recodes missing values to NA. The function takes a dataframe with variables with missing data, and specified values of missing data
recode_missing_df <- function(df, missing_vals = c(90, 95, 99)) {
  modify(df, ~recode_missing(.x, missing_vals)) # here uses the function created above
}

selected_data1 <- recode_missing_df(selected_data1) %>%
  drop_na() %>%
  mutate(ACE = factor(ace2more_1718),
         ACE = recode_factor(ACE,
                          "2" = "Exp 1 ACE",
                          "3" = "Exp 2 Ace"))

selected_data1 <- selected_data1 %>%
  group_by(state, ACE) %>%
  count(ACE)

selected_data1 <- selected_data1 %>%
  group_by(state) %>%
  mutate(tot = sum(n))

# Creating a column for label

library(english)
library(glue)
selected_data1 <- selected_data1 %>%
  mutate(label =
  glue("{str_to_title(as.english(tot))} Children experienced ACE"))


# Plot for one state

selected_data1 %>%
  filter(state == "Alabama")

ggplot(selected_data1, aes(ACE, n)) +
  geom_col(aes(fill = n)) +
  scale_fill_distiller(type = "seq",
                       limits = c(0, max(selected_data1$n)),
                       palette = "BuPu",
                       direction = 1) +
  ylim(0, max(selected_data1$n)) +
  coord_flip() +
  labs(title = "Number of children experienced ACE : Alabama",
       x = "Adverse Childhood Experience",
       y = "Number of children under 5s",
       caption = unique(selected_data1$label))

#Produce plots for 51 states using pmap
final_plots <- selected_data1 %>%
  group_by(state, label) %>%
  nest() %>%
  mutate(plots = pmap(list(state, label, data),
                      ~ggplot(..3, aes(ACE, n)) +
                        geom_col(aes(fill = n)) +
                        scale_fill_distiller(type = "seq",
                                             limits = c(0, max(selected_data1$n)),
                                             palette = "BuPu",
                                             direction = 1) +
                        ylim(0, max(selected_data1$n)) +
                        coord_flip() +
                        labs(title = glue("Number of children experienced ACE : {..1}"),
                             x = "Adverse Childhood Exp",
                             y = "Number of Children",
                             caption = ..2)))
final_plots$plots[[5]]
# Create directory to save plots

fs::dir_create(here::here("plots", "selected_data1"))

# Create file path
files <- str_replace_all(tolower(final_plots$state), " ", "-")
paths <- here::here("plots", "selected_data1", glue("{files}.png"))
paths

#save plots
walk2(paths, final_plots$plots, ggsave,
      width = 9.5, 
      height = 6.5,
      dpi = 500)
```
                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           
