
---
title: "spring20_finalproject"
author: "Asha Yadav, Alejandra Garcia Isaza, and Mark Hammond"
date: "4/28/2020"
output: html_document
---

We are using the National Survey of Children’s Health (NSCH) data. This nationally representative dataset includes information on multiple variables related to child health and wellbeing for non-institutionalized children between zero and seventeen years of age across the United States. It includes variables on domains such as physical health, mental health, access and quality to health care services, and the ecological contexts in which the child develops (family, neighborhoods, school, and social environments). 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rio)
library(here)
library(english)
library(glue)
library(fs)

theme_set(theme_minimal())
```


```{r, data}
# Batch loading
#files <- dir_ls(here::here("data"), glob = "*.csv")

#batch <- map_df(files, read_csv)
#batch

# importing the data
NCSH <- import(here("data","2017-2018 NSCH_Topical_DRC_Dec 2019.csv"), setclass = "tbl_df")
state <- import(here("data","fips_state.csv"))

# Left_join to add states in the NCSH dataset
final_data <- left_join(NCSH, state, by = "FIPSST")

# alternative way for cases in which there are more than 2 files
# files <- dir_ls(here::here("data"), glob = "*.csv")
# 
# batch <- map(files, read_csv)
#
# reduce(batch, left_join, by = "FIPSST")
```


```{r, data prep}

selected_data <- final_data %>%
  select(HHID, HHLANGUAGE, SC_AGE_YEARS, SC_SEX, MOMAGE, HHCOUNT, K6Q20, K11Q60, K11Q61, K11Q62, S9Q34, K10Q14, ACE1, ACE3, ACE4, ACE5, ACE6, ACE7, ACE8, ACE9, ACE10, RECOGABC, A1_GRADE, A2_GRADE, K6Q60_R, K6Q61_R, FOODSIT, K8Q30, CONFIDENT, povlev4_1718, AdultEduc_1718, WrkngPoor_1718, ACEct_1718, ACE2more_1718, State) %>%
  janitor::clean_names() %>% # cleaning names
  filter(sc_age_years == 5) # filtering data
```

```{r, function 1}
# Function to recode missing data

# vector with missing values in my dataset
missing_vals <- c(90, 95, 99)

# function that returns true if values in vector are equal to missing_vals. The function takes a vector x, and specified values of missing data
recode_missing <- function(x, missing_vals = c(90, 95, 99)) {
  test <- x %in% missing_vals
  ifelse(test, NA, x)
}

# function that recodes missing values to NA. The function takes a dataframe with variables with missing data, and specified values of missing data
recode_missing_df <- function(df, missing_vals = c(90, 95, 99)) {
  modify(df, ~recode_missing(.x, missing_vals)) # here uses the function created above
}
```


```{r, data cleaning}

d <- recode_missing_df(selected_data) %>%
  drop_na() %>% # dropping cases with missing data
  mutate(confident = factor(confident),
         confident = fct_recode(confident,
                           "Completely confident" = "1",
                           "Mostly confident" = "2",
                           "Somewhat confident" = "3",
                           "Not at all confident" = "4"),
         how_well_demands = factor(k8q30),
         how_well_demands = fct_recode(how_well_demands,
                           "Very well" = "1",
                           "Somewhat well" = "2",
                           "Not very well" = "3",
                           "Not at all" = "4"),
         primary_cg_ed = factor(a1_grade),
         primary_cg_ed = fct_recode(primary_cg_ed,
                           "8th grade or less" = "1",
                           "9th-12th grade; No diploma" = "2",
                           "High School Graduate or GED" = "3",
                           "Vocational, trade, or business school program" = "4",
                           "Some College Credit, no Degree" = "5",
                           "Associate Degree" = "6",
                           "Bachelor’s Degree" = "7",
                           "Master’s Degree" = "8",
                           "Doctorate" = "9"),
         home_language = factor(hhlanguage),
         home_language = fct_recode(home_language,
                          "English" = "1",
                          "Spanish" = "2",
                          "Other" = "3"),
         child_sex = factor(sc_sex),
         child_sex = fct_recode(child_sex,
                          "Male" = "1",
                          "Female" = "2"),
         child_age = sc_age_years,
         ACE = factor(ace2more_1718),
         ACE = fct_recode(ACE,
                          "Exp 1 ACE" = "2",
                          "Exp 2 ACE" = "3"),
         stories_songs = factor(k6q61_r),
         read = factor(k6q60_r)) %>% 
  mutate_at(c("stories_songs","read"), ~(fct_recode(., 
                                              "0 days" = "1",
                                              "1-3 days" = "2",
                                              "4-6 days" = "3",
                                              "Every day" = "4"))) %>%
  select(hhid, child_sex, child_age, home_language, stories_songs, read, confident, how_well_demands, primary_cg_ed, ACE, state)


#Akhila's function suggestion:

d1 <- recode_missing_df(selected_data) %>%
 drop_na() %>% 
  mutate_at(vars("k6q61_r":"k6q60_r"), 
            funs(factor(.,
                        levels = c(
                          "0 days",
                          "1-3 days",
                          "4-6 days",
                          "Everyday"),
                        ordered = TRUE)))



```


```{r}
d %>%
  map()

```


```{r, function 2}
# add this to the shiny app so peep can interact and change the variables from a drop down menu
bar_plot <- function(df, x) {
  plot_graph <- ggplot(df, aes({{x}})) +
    geom_bar(aes(fill = {{x}}), show.legend = FALSE) +
    coord_flip()
  
  if(!as.numeric(pull(df, {{x}}))) {
    stop()
  }
  else{
    plot_graph
  }
  return(plot_graph)
}

bar_plot(d, read) +
  labs(x = 'Number of days reading',
       title = 'Confidence in kindergarten readiness by frequency of reading at home') +
facet_wrap(~confident)
```


* Examining 'Confidence in School Readiness' by 'Caregiver's Highest Level of Education'

```{r}
plot1_df <- d %>%
  group_by(state, primary_cg_ed) %>%
  count(confident) %>% 
  mutate(prop_conf = round(n/sum(n), digits = 2)) %>%  
  mutate(label =
        glue("NCES Data from {str_to_title(state)}"))

plot1 <- plot1_df  %>%
  group_by(state, label) %>%
  nest() %>%
  mutate(plots = pmap(list(state, label, data),
                      ~ggplot(..3, aes(primary_cg_ed, prop_conf, fill = confident)) +
                      geom_bar(stat = "identity", position = "dodge") +
                      coord_flip() +
                      labs(title = glue("Confidence in School Preparedness Between \nLevels of Caregiver Education: {..1}"),
                             x = "Caregiver's Highest Level of Education",
                             y = "Proportion of Parents",
                             caption = ..2)))
plot1$plots[[20]]
```

Saving plots for examining 'Confidence in School Readiness' by 'Caregiver's Highest Level of Education'

```{r}
# Creating directory to save plots

fs::dir_create(here::here("plots", "plot1"))

# Creating file path
files <- str_replace_all(tolower(plot1$state), " ", "-")
paths <- here::here("plots", "plot1", glue("schl-conf-and-edlevel-by-state_{files}.png"))
paths

#saving plots
walk2(paths, plot1$plots, ggsave,
      width = 9.5, 
      height = 6.5,
      dpi = 500)
```








