---
title: "spring20_finalproject"
author: "Asha Yadav"
date: "4/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rio)
library(here)

theme_set(theme_minimal())
```

```{r}
# importing the data
d <- import(here("data", "2017-2018 NSCH_Topical_DRC_Dec 2019.csv"), setclass = "tbl_df") 
```

Final Project Components

* No code is used repetitively (no more than twice) [10 points]
* More than one variant of purrr::map is used [10 points]
* At least one {purrr} function outside the basic map family (walk_*, reduce, modify_*, etc.) [10 points]
* At least one instance of parallel iteration (e.g., map2_*, pmap_*) [10 points]
* At least one use case of purrr::nest %>% mutate() [10 points]
* At least two custom functions [20 points; 10 points each]
  ** Each function must do exactly one thing
  ** The functions may replicate the behavior of a base function - as noted above this is about practicing the skills you learn in class
* Code is fully reproducible and housed on GitHub [10 points]
* No obvious errors in chosen output format [10 points]
* Deployed on the web and shareable through a link [10 points]
