---
title: "spring20_finalproject"
author: "Asha Yadav, Alejandra Garcia Isaza, and Mark Hammond"
date: "4/28/2020"
output: html_document
---

We are using the National Survey of Children’s Health (NSCH) data. This nationally representative dataset includes information on multiple variables related to child health and wellbeing for non-institutionalized children between zero and seventeen years of age across the United States. It includes variables on domains such as physical health, mental health, access and quality to health care services, and the ecological contexts in which the child develops (family, neighborhoods, school, and social environments). 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rio)
library(here)
library(english)
library(glue)

theme_set(theme_minimal())
```

```{r, data}
# importing the data

NCSH <- import(here("data","2017-2018 NSCH_Topical_DRC_Dec 2019.csv"), setclass = "tbl_df")
state <- import(here("data","fips_state.csv"))
#Left_join to add states in the NCSH dataset
final_data <- left_join(NCSH, state, by = "FIPSST")

```

```{r}
# data prep
selected_data <- final_data %>%
  select(HHID, HHLANGUAGE, SC_AGE_YEARS, SC_SEX, MOMAGE, HHCOUNT, K6Q20, K11Q60, K11Q61, K11Q62, S9Q34, K10Q14, ACE1, ACE3, ACE4, ACE5, ACE6, ACE7, ACE8, ACE9, ACE10, RECOGABC, A1_GRADE, A2_GRADE, K6Q60_R, K6Q61_R, FOODSIT, K8Q30, CONFIDENT, povlev4_1718, AdultEduc_1718, WrkngPoor_1718, ACEct_1718, ACE2more_1718, State) %>%
  janitor::clean_names() %>% # cleaning names
  filter(sc_age_years <= 5, ace2more_1718 > 1) # filtering data
```

```{r, function 1}
# Function to recode missing data

# vector with missing values in my dataset
missing_vals <- c(90, 95, 99)

# function that returns true if values in vector are equal to missing_vals. The function takes a vector x, and specified values of missing data
recode_missing <- function(x, missing_vals = c(90, 95, 99)) {
  test <- x %in% missing_vals
  ifelse(test, NA, x)
}

# function that recodes missing values to NA. The function takes a dataframe with variables with missing data, and specified values of missing data
recode_missing_df <- function(df, missing_vals = c(90, 95, 99)) {
  modify(df, ~recode_missing(.x, missing_vals)) # here uses the function created above
}
```

```{r}
d1 <- recode_missing_df(selected_data) %>%
 drop_na() %>% 
  mutate_at(vars(k6q61_r, k6q60_r), 
            funs(factor(.,
                        levels = c(
                          "0 days",
                          "1-3 days",
                          "4-6 days",
                          "Everyday"),
                        ordered = TRUE)))

```


```{r}
# more data cleaning


d <- recode_missing_df(selected_data) %>%
  drop_na() %>% # dropping cases with missing data
  mutate(stories_songs = factor(k6q61_r),
         stories_songs = fct_recode(stories_songs,
                           "0 days" = "1",
                           "1-3 days" = "2",
                           "4-6 days" = "3",
                           "Every day" = "4"),
         read = factor(k6q60_r),
         read = fct_recode(read,
                           "0 days" = "1",
                           "1-3 days" = "2",
                           "4-6 days" = "3",
                           "Every day" = "4"),
         confident = factor(confident),
         confident = fct_recode(confident,
                           "Completely confident" = "1",
                           "Mostly confident" = "2",
                           "Somewhat confident" = "3",
                           "Not at all confident" = "4"),
         how_well_demands = factor(k8q30),
         how_well_demands = fct_recode(how_well_demands,
                           "Very well" = "1",
                           "Somewhat well" = "2",
                           "Not very well" = "3",
                           "Not at all" = "4"),
         primary_cg_ed = factor(a1_grade),
         primary_cg_ed = fct_recode(primary_cg_ed,
                           "8th grade or less" = "1",
                           "9th-12th grade; No diploma" = "2",
                           "High School Graduate or GED" = "3",
                           "Vocational, trade, or business school program" = "4",
                           "Some College Credit, no Degree" = "5",
                           "Associate Degree" = "6",
                           "Bachelor’s Degree" = "7",
                           "Master’s Degree" = "8",
                           "Doctorate" = "9"),
         home_language = factor(hhlanguage),
         home_language = fct_recode(home_language,
                          "English" = "1",
                          "Spanish" = "2",
                          "Other" = "3"),
         child_sex = factor(sc_sex),
         child_sex = fct_recode(child_sex,
                          "Male" = "1",
                          "Female" = "2"),
         child_age = sc_age_years,
         ACE = factor(ace2more_1718),
         ACE = fct_recode(ACE,
                          "Exp 1 ACE" = "2",
                          "Exp 2 ACE" = "3")) %>%
  select(hhid, child_sex, child_age, home_language, stories_songs, read, confident, how_well_demands, primary_cg_ed, ACE, state)
```



```{r, function 2}
bar_plot <- function(df, x) {
  plot_graph <- ggplot({{df}}, aes({{x}})) +
    geom_bar(aes(fill = x), show.legend = FALSE) +
    coord_flip()
  
  if(!as.numeric({{x}})) {
    stop()
  }
  else{
    plot_graph
  }
  return(plot_graph)
}

bar_plot(d, d$read) +
  labs(x = 'Number of days reading',
       y = 'Count') +
  facet_wrap(~confident)
  

```

* Plots looking at number of children experiencing Adverse Childhood Experiences (ACE) in US states 

```{r}
# counting number of ACEs
d2 <- d %>%
  group_by(state, ACE) %>%
  count(ACE) %>%
  group_by(state) %>%
  mutate(tot = sum(n))

# Creating a column for label
d2 <- d2 %>%
  mutate(label =
  glue("{str_to_title(as.english(tot))} Children experienced ACE"))

# Plot for one state
plot_alabama <- d2 %>%
  filter(state == "Alabama") %>%
  ggplot(aes(ACE, n)) +
  geom_col(aes(fill = n)) +
  scale_fill_distiller(type = "seq",
                       limits = c(0, max(d2$n)),
                       palette = "BuPu",
                       direction = 1) +
  ylim(0, max(d2$n)) +
  coord_flip() +
  labs(title = "Number of children that experienced ACEs: Alabama",
       x = "Adverse Childhood Experiences",
       y = "Number of children",
       caption = unique(d2$label))

#Producing plots for 51 states using pmap
final_plots <- d2 %>% 
  group_by(state, label) %>%
  nest() %>%
  mutate(plots = pmap(list(state, label, data),
                      ~ggplot(..3, aes(ACE, n)) +
                        geom_col(aes(fill = n)) +
                        scale_fill_distiller(type = "seq",
                                             limits = c(0, max(d2$n)),
                                             palette = "BuPu",
                                             direction = 1) +
                        ylim(0, max(d2$n)) +
                        coord_flip() +
                        labs(title = glue("Number of children that experienced ACEs: {..1}"),
                             x = "Adverse Childhood Experiences",
                             y = "Number of Children",
                             caption = ..2)))
final_plots$plots[[5]]

# Creating directory to save plots
fs::dir_create(here::here("plots", "d2"))

# Creating file path
files <- str_replace_all(tolower(final_plots$state), " ", "-")
paths <- here::here("plots", "d2", glue("{files}.png"))
paths

# saving plots
walk2(paths, final_plots$plots, ggsave,
      width = 9.5, 
      height = 6.5,
      dpi = 500)
```

* Examining 'Confidence in School Readiness' by 'Caregiver's Highest Level of Education'

```{r}
plot1_df <- d %>%
  group_by(state, primary_cg_ed) %>%
  count(confident) %>% 
  mutate(prop_conf = round(n/sum(n), digits = 2)) %>%  
  mutate(label =
        glue("NCES Data from {str_to_title(state)}"))

plot1 <- plot1_df  %>%
  group_by(state, label) %>%
  nest() %>%
  mutate(plots = pmap(list(state, label, data),
                      ~ggplot(..3, aes(primary_cg_ed, prop_conf, fill = confident)) +
                      geom_bar(stat = "identity", position = "dodge") +
                      coord_flip() +
                      labs(title = glue("Confidence in School Preparedness Between \nLevels of Caregiver Education: {..1}"),
                             x = "Caregiver's Highest Level of Education",
                             y = "Proportion of Parents",
                             caption = ..2)))
plot1$plots[[1]]

```

Saving plots for examining 'Confidence in School Readiness' by 'Caregiver's Highest Level of Education'

```{r}
# Creating directory to save plots

fs::dir_create(here::here("plots", "plot1"))

# Creating file path
files <- str_replace_all(tolower(plot1$state), " ", "-")
paths <- here::here("plots", "plot1", glue("schl-conf-and-edlevel-by-state_{files}.png"))
paths

#saving plots
walk2(paths, plot1$plots, ggsave,
      width = 9.5, 
      height = 6.5,
      dpi = 500)
```

* Examining'Confidence in School Readiness' by 'Frequency of Reading at Home'

```{r}

plot2_df <- d %>%
  group_by(primary_cg_ed, home_language, read) %>%
  count(confident) %>% 
  mutate(perc_conf = 100*(round(n/sum(n), digits = 2))) %>%
  mutate(label =
        glue("NCES Data for parents reporting '{str_to_title(primary_cg_ed)}'"))

plot2 <- plot2_df  %>%
  group_by(primary_cg_ed, label) %>%
  nest() %>%
  mutate(plots = pmap(list(primary_cg_ed, label, data),
                      ~ggplot(..3, aes(read, perc_conf, fill = confident)) +
                      geom_bar(stat = "identity", position = "dodge") +
                      coord_flip() +
                      labs(title = "Confidence in School Preparedness Between \nLevels Frequency of Reading at Home",
                           subtitle = glue("Caregiver Education Level: '{..1}'"),
                             x = "Frequency of Reading at Home",
                             y = "Percentage of Parent Reports",
                             caption = ..2)))
plot2$plots[[5]]

```

Saving plots for examining 'Confidence in School Readiness' by 'Frequency of Reading at Home'

```{r}
# Creating directory to save plots
fs::dir_create(here::here("plots", "plot2"))

# Creating file path
files <- str_replace_all(tolower(plot2$primary_cg_ed), " ", "-")
paths <- here::here("plots", "plot2", glue("schl-conf-and-read-by-edlevel_{files}.png"))
paths

#saving plots
walk2(paths, plot2$plots, ggsave,
      width = 9.5, 
      height = 6.5,
      dpi = 500)
```
